Data preparation

### 2020-04-07 production/prod_prep-data-A.rmd
data preparation

---
title: "Data preparation"
date: "`r format(Sys.time(), '%d %B, %Y')`"
css: "../input/bib/style.css"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_float: false
    toc_depth: 2
    code_folding: "hide"
editor_options: 
  chunk_output_type: console
---

>>>>

title: ---"Data preparation"
date: "`r format(Sys.time(), '%d %B, %Y')`"
css: "../input/bib/style.css"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_float: false
    toc_depth: 2
    code_folding: "hide"
editor_options: 
  chunk_output_type: console
---
